---
title: "StudyB_2/2"
output: html_notebook
---


#Importing libs
```{r}
library(dplyr)
library(fitdistrplus)
library(rstatix)
library(readxl)
library(lme4)
library(multcomp)
library(lsmeans)
library(car)
library(flexplot)
library(ggplot2)
library(tidyverse)
library(ggpubr)
library(ggprism)
library(reshape2)
library(ARTool)
```
# In which movement mode was it easier to read?
## Preparing the data
- Reading data
```{r}
readingPhra <- read_excel("./data/StudyB_Data.xlsx", sheet = "PHRA_Details")
```
- Formatting data
```{r}
USER=readingPhra["USER"]
FS=readingPhra["FONT_SIZE"]
Q1=readingPhra["Q1"]
FT=readingPhra["FONT_TYPE"]
ROTATION=readingPhra["ROTATION_C"]

prefsData=data.frame(USER,FS,FT,ROTATION,Q1)

prefsData$USER=as.factor(as.numeric(prefsData$USER)-12)


prefsData$FONT_SIZE=as.factor(as.numeric(prefsData$FONT_SIZE)/4)
prefsData$FONT_TYPE=as.factor(prefsData$FONT_TYPE)
prefsData$ROTATION_C=as.factor(prefsData$ROTATION_C)
prefsData$Q1=as.factor(prefsData$Q1)


summary(prefsData)
```
- Summarizing data
```{r}
easier2read=prefsData%>%
  group_by(USER,Q1, FONT_TYPE, FONT_SIZE)%>%
  summarise(Counts=n())
summary(easier2read)
```

- Inserting 0 values missing
```{r}
easier2read_complete=dcast(easier2read, USER+FONT_TYPE+ FONT_SIZE~Q1, value.var="Counts",  fun.aggregate=sum)
```

```{r}
easier2read_complete = easier2read_complete%>%
  gather(key = "Q1", value = "Counts", Circular,Linear, Same, Static)
```
- Filtering out SAME responses

```{r}
easier2read_NOSAME=easier2read_complete%>%
  filter(Q1!="Same")
easier2read_NOSAME$Q1=as.factor(easier2read_NOSAME$Q1)
summary(easier2read_NOSAME)
```
- Data visualization

```{r fig12_3,fig.width=9, fig.height=4,fig.align='center'}
ggplot(data=easier2read_NOSAME, aes(x=FONT_SIZE,y=Counts, color=Q1))+
  geom_boxplot(outlier.colour="blue", outlier.shape=16,
             outlier.size=2)+
 stat_summary(fun = mean,
              aes(group=Q1, col=Q1),
              position=position_dodge(width=0.75),
              color = "red") +
  stat_summary(
    fun.min = function(x) mean(x) - sd(x),
    fun.max = function(x) mean(x) + sd(x),
    geom = "errorbar",
    color = "red",
    width = .3,
    alpha=0.5,
    aes(group=Q1, col=Q1) , position=position_dodge(width=0.75)
  
  )+
  xlab("Movement mode")+
  ylab("Votes")+
  facet_grid(rows=vars(FONT_TYPE))
 
```

```{r fig13_3,fig.width=9, fig.height=4,fig.align='center'}
ggplot(easier2read_NOSAME, aes(x=Counts, fill=FONT_TYPE))+
  geom_histogram(binwidth=1)+
  facet_grid(~FONT_SIZE~Q1+FONT_TYPE)
```



## GLMM Binomial 


- Building model
```{r}
mEasier=glmer(cbind(Counts,4-Counts)~Q1*FONT_SIZE*FONT_TYPE +(1|USER), data = easier2read_NOSAME, family = binomial(link="logit"), nAGQ = 100, contrast=list(FONT_TYPE="contr.sum",FONT_SIZE="contr.sum",Q1="contr.sum" ))
```

## Anova

```{r}
Anova(mEasier, type=3)
```

## PWC


- MOVEMENT MODE
- Rebuilding the model 
```{r}
mMOV=glmer(cbind(Counts,4-Counts)~Q1+(1|USER), data = easier2read_NOSAME, family = binomial(link="logit"), nAGQ = 100, contrast=list(Q1="contr.sum" ))
summary(mMOV)
```
- Comparing pairs
```{r}
summary(glht(mMOV,lsm(pairwise~Q1)),test=adjusted(type="bonferroni"))
```

- Manually handeling results for ploting
```{r}
pwcMOVPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,~FONT_SIZE,~C1,~C2,~xmin,~xmax,
  "Circular", "Linear", "*", 4.5,2,0,0,1,2,
  "Circular", "Static", "***", 5,2,0,0,1,3,
  "Linear", "Static", "***", 5.5,2,0,0,2,3,
)
  
```



- MOVEMENT MODE : FONT SIZE

```{r}
mQS=glmer(cbind(Counts,4-Counts)~Q1*FONT_SIZE+(1|USER), data = easier2read_NOSAME, family = binomial(link="logit"), nAGQ = 100, contrast=list(Q1="contr.sum" ,FONT_SIZE="contr.sum" ))
```

- Programatically get the PWC values

```{r}


pwcQSIZEPlot=tidy(summary(glht(mQS,lsm(pairwise~Q1*FONT_SIZE)),test=adjusted(type="bonferroni"))
)
##Adding starts

pwcQSIZEPlot$p.signif=symnum(pwcQSIZEPlot$adj.p.value, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("***", "**", "*", ".", " "))
pwcQSIZEPlot$row_num <- seq.int(nrow(pwcQSIZEPlot))

##Adding groups
pwcQSIZEPlot$group1=sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',1)
pwcQSIZEPlot$group2=sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',4)
pwcQSIZEPlot$C1=as.numeric(sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',2))
pwcQSIZEPlot$C2=as.numeric(sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',5))

##Adding   xmin and xman
pwcQSIZEPlot= pwcQSIZEPlot %>% 
  mutate(xmin = case_when(C1==8~1,C1==10~2,C1==12~3))%>%
  mutate(xmin = case_when(group1=="Circular"~xmin-0.25,group1=="Linear"~xmin,group1=="Static"~xmin+0.25))

pwcQSIZEPlot= pwcQSIZEPlot %>% 
  mutate(xmax = case_when(C2==8~1,C2==10~2,C2==12~3))%>%
  mutate(xmax= case_when(group2=="Circular"~xmax-0.25,group2=="Linear"~xmax,group2=="Static"~xmax+0.25))

## Not significatt values fitered out
pwcQSIZEPlot=pwcQSIZEPlot%>%
  filter(adj.p.value<0.05)

## Not same font size
pwcQSIZEPlot=pwcQSIZEPlot%>%
  filter(C1==C2 | group1 ==group2)


## Ordering by movement
pwcQSIZEPlot=pwcQSIZEPlot[order(pwcQSIZEPlot[,11],pwcQSIZEPlot[,11]),]

pwcQSIZEPlot= pwcQSIZEPlot %>% 
  mutate(color = case_when(C1==8 & C2==8~"8",C1==10& C2==10~"10",C1==12 & C2==12~"12", C1!=C2~"MX"))



##  add y.posision
#pwcQSIZEPlot$y.position <- seq.int(4.5, by=0.2, length.out = dim(pwcQSIZEPlot)[1])

pwcQSIZEPlot=pwcQSIZEPlot%>%
  group_by(color)%>%
  mutate(y.position = case_when(
    color=="MX"~seq.int(9.5, length.out=length(color),by=0.2),
    color!="MX"~seq.int(8, length.out=length(color),by=0.2)))

pwcQSIZEPlot
```


## Plots

```{r}
pwcMOVPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,~FONT_SIZE,~C1,~C2,~xmin,~xmax,
  "Circular", "Linear", "*", 4.5,2,0,0,1,2,
  "Circular", "Static", "***", 5,2,0,0,1,3,
  "Linear", "Static", "***", 5.5,2,0,0,2,3,
)

movPLot=easier2read_NOSAME%>%
  group_by(USER,Q1)%>%
  summarise(Count=sum(Counts))%>%
  ggplot(aes(x=Q1,y=Count,  fill=Q1))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line",linetype="dashed", aes(group = 1)) + 
  stat_summary( color = "red",size = 0.3, aes(group = 1), size = 0.5)+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x=NA,y="Cummulative votes")+
  ylim(0,25)+
  add_pvalue(inherit.aes = FALSE,pwcMOVPlot,
             bracket.size = 0.6,
             tip.length = 0.01,
             colour = "magenta",
             label.size = 2)

movPLot



movfsPlot=easier2read_NOSAME%>%
  group_by(USER,Q1,FONT_SIZE)%>%
  summarise(Count=sum(Counts))%>%
  ggplot(aes(x=FONT_SIZE,y=Count,  fill=Q1))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary( aes(group=Q1),
                position=position_dodge(width=0.75),color = "red", geom = "line", linetype="dashed") + 
  stat_summary( color = "red", size = 0.3,aes(group=Q1),
                position=position_dodge(width=0.75))+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  
  labs(x="Movement",y="Cummulative votes")+
  ylim(0,10)+
  add_pvalue(inherit.aes=FALSE,pwcQSIZEPlot,
             xmin = "xmin",
             xmax="xmax",
             bracket.size = 0.5,
             tip.length = 0.01,
             colour = "magenta",
             label.size=2)

movfsPlot

figure1 <- ggarrange(movPLot,movfsPlot,
                     ncol = 2, nrow = 1)
figure1
```

# Minimum and Comforatble Font Size
## Minimum size
### Importing data
```{r}
##PLotting
phraMinFile <- read_excel("./data/StudyB_Data.xlsx", sheet = "PHRA_FontSize")
```

- Raw data
```{r}
USER=phraMinFile["USER"]
FT=phraMinFile["FONT_TYPE"]
MIN_FS=phraMinFile["MIN_FS"]
CONF_FS=phraMinFile["CONF_FS"]
MOVEMENT=phraMinFile["MOVEMENT"]

data= data.frame(USER,FT,MOVEMENT,MIN_FS, CONF_FS)
data$USER <- as.factor(data$USER)
data$FONT_TYPE <- as.factor(data$FONT_TYPE)
data$MOVEMENT <- as.factor(data$MOVEMENT)
data$MIN_FS <- as.numeric(data$MIN_FS)
data$CONF_FS <- as.numeric(data$CONF_FS)
data$MIN=as.numeric(data$MIN_FS/4)
data$CONF=as.numeric(data$CONF_FS/4)

summary(data)
```

- Formatting data per user

```{r}
uData=data%>%
 group_by(USER,MOVEMENT,FONT_TYPE)%>%
  summarise(MeanMin=mean(MIN), StdMin=sd(MIN),MeanConf=mean(CONF), StdConf=sd(CONF))
summary(uData)
```
```{r}
uData%>%
  group_by(FONT_TYPE)
```


- Visualization 

```{r}
meanLines= uData%>%
  group_by(MOVEMENT, FONT_TYPE)%>%
  summarize(Mean=mean(MeanMin))

ggplot(data= uData,aes(x=MeanMin))+
  geom_vline(data=meanLines,mapping= aes(xintercept=Mean),
                            color="red", linetype="dashed", size=0.5)+
   geom_histogram(aes(y=..density..), colour="black", fill="white",binwidth = 0.5)+
   geom_density(alpha=.2, fill="#FF6666")+
  labs(title = "Minimum font size distribution")+
  xlab("Font size")+
  ylab("Density")+
  facet_grid(~FONT_TYPE~MOVEMENT)
```
```{r}
ggplot(uData, aes(FONT_TYPE,MeanMin, color=MOVEMENT))+
  geom_boxplot()
```


- FIT
```{r}
goft::gamma_test(uData[uData$MOVEMENT=="circular" & uData$FONT_TYPE=="A",]$MeanMin)
goft::gamma_test(uData[uData$MOVEMENT=="circular" & uData$FONT_TYPE=="T",]$MeanMin)
goft::gamma_test(uData[uData$MOVEMENT=="linear" & uData$FONT_TYPE=="A",]$MeanMin)
goft::gamma_test(uData[uData$MOVEMENT=="linear" & uData$FONT_TYPE=="T",]$MeanMin)
goft::gamma_test(uData[uData$MOVEMENT=="static" & uData$FONT_TYPE=="A",]$MeanMin)
goft::gamma_test(uData[uData$MOVEMENT=="static" & uData$FONT_TYPE=="T",]$MeanMin)
```



### GLMM Gamma

- Buillding the model
```{r}
mMINFULL=glmer(MeanMin~MOVEMENT*FONT_TYPE + (1| USER), data = uData, family = Gamma(link = "log"), nAGQ = 2, contrasts = list(MOVEMENT="contr.sum",FONT_TYPE="contr.sum" ))
summary(mMINFULL)
```
### Anova
```{r}
Anova(mMINFULL, type=3)
#Add statrisics of almost significant ANova
```


## Comfortabl size (Optimmal)

- Visualization 

```{r}
meanLines= uData%>%
  group_by(MOVEMENT, FONT_TYPE)%>%
  summarize(Mean=mean(MeanConf))

ggplot(data= uData,aes(x=MeanConf))+
  geom_vline(data=meanLines,mapping= aes(xintercept=Mean),
                            color="red", linetype="dashed", size=0.5)+
   geom_histogram(aes(y=..density..), colour="black", fill="white",binwidth = 0.5)+
   geom_density(alpha=.2, fill="#FF6666")+
  labs(title = "Minimum font size distribution")+
  xlab("Font size")+
  ylab("Density")+
  facet_grid(~FONT_TYPE~MOVEMENT)
```
```{r}
ggplot(uData, aes(FONT_TYPE,MeanConf, color=MOVEMENT))+
  geom_boxplot()
```

- FTI

```{r}
goft::gamma_test(uData[uData$MOVEMENT=="circular" & uData$FONT_TYPE=="A",]$MeanConf)
goft::gamma_test(uData[uData$MOVEMENT=="circular" & uData$FONT_TYPE=="T",]$MeanConf)
goft::gamma_test(uData[uData$MOVEMENT=="linear" & uData$FONT_TYPE=="A",]$MeanConf)
goft::gamma_test(uData[uData$MOVEMENT=="linear" & uData$FONT_TYPE=="T",]$MeanConf)
goft::gamma_test(uData[uData$MOVEMENT=="static" & uData$FONT_TYPE=="A",]$MeanConf)
goft::gamma_test(uData[uData$MOVEMENT=="static" & uData$FONT_TYPE=="T",]$MeanConf)
```



### GLMM Gamma
- Building the model
```{r}
mCONFFULL=glmer(MeanConf~MOVEMENT*FONT_TYPE + (1| USER), data = uData, family = Gamma(link = "log"), nAGQ = 1, contrasts = list(MOVEMENT="contr.sum",FONT_TYPE="contr.sum" ))
summary(mMINFULL)
```
### Anova
```{r}
Anova(mCONFFULL, type=3)
```

### PWC
- Rebuild the model
```{r}
mCONFMOV=glmer(MeanConf~MOVEMENT + (1| USER), data = uData, family = Gamma(link = "log"), nAGQ = 1, contrast =list(MOVEMENT="contr.sum"))
summary(mCONFMOV)
```
- Get PWC
```{r}
summary(glht(mCONFMOV,lsm(pairwise~MOVEMENT)),test=adjusted(type="bonferroni"))
```
- Manually handle output
```{r}
pwcCONFMOV=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,~FONT_SIZE,~C1,~C2,~xmin,~xmax,
  "circular", "linear", "*", 13,2,0,0,1,2,
  "circular", "static", "***", 13.8,2,0,0,1,3,
  "linear", "static", "***", 14,2,0,0,2,3,
)
  
```

## Plots
```{r}
minAllPlot=uData%>%
  group_by(USER,MOVEMENT, FONT_TYPE)%>%
  summarise(MEAN=mean(MeanMin))%>%
  ggplot(aes(MOVEMENT:FONT_TYPE,MEAN,fill=MOVEMENT))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype = "dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1),)+  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x="Movement",y="Font size")+
  ylim(0,14)

minAllPlot


uData%>%
  group_by(MOVEMENT)%>%
  summarise(MEAN=mean(MeanMin), STD=sd(MeanMin))


uData%>%
  group_by(MOVEMENT)%>%
  summarise(M=mean(MeanConf), S=sd(MeanConf))



minPlot=uData%>%
  group_by(USER,MOVEMENT)%>%
  summarise(MEAN=mean(MeanMin))%>%
  ggplot(aes(MOVEMENT,MEAN,fill=MOVEMENT))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype = "dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1),)+  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x="Movement",y="Font size")+
  #add_pvalue(inherit.aes = FALSE,pwcMINMOV,
    #         bracket.size = 0.6,
     #        tip.length = 0.01,
     #        colour = "magenta",
     #        label.size = 2)+
  ylim(0,14)

minPlot



confAllPlot=uData%>%
  group_by(USER,MOVEMENT, FONT_TYPE)%>%
  summarise(MEAN=mean(MeanConf))%>%
  ggplot(aes(MOVEMENT:FONT_TYPE,MEAN,fill=MOVEMENT))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype = "dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1),)+  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x="Movement",y="Font size")+
  ylim(0,14)

confAllPlot


confPlot=uData%>%
  group_by(USER,MOVEMENT)%>%
  summarise(MEAN=mean(MeanConf))%>%
  ggplot(aes(MOVEMENT,MEAN,fill=MOVEMENT))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype = "dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1), size = 0.5)+  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x="Movement",y="Font size")+
  ylim(0,14)+
  add_pvalue(inherit.aes = FALSE,pwcCONFMOV,
             bracket.size = 0.6,
             tip.length = 0.01,
             colour = "magenta",
             label.size = 2)

confPlot


figure1 <- ggarrange(minAllPlot, confAllPlot,minPlot,confPlot,
                     ncol = 4, nrow = 1)
figure1

```

