---
title: "StudyD"
output: html_notebook
---
# Import libs
```{r}
library(ggpubr)
library(tidyverse)
library(ggplot2)
library(readxl)
library(rstatix)
library(emmeans)
library(dplyr)
library(tibble)
library(fitdistrplus)
library(lme4)
library(multcomp)
library(lsmeans)
library(car)
```

# Reading on Pinhole Paper

## Importing data
```{r}
readingReal=read_excel("./data/StudyD_Data.xlsx", sheet = "Reading")
```

- Data overview
```{r}
user=readingReal["user"]
min=readingReal["min"]
conf=readingReal["conf"]
ft=readingReal["font_type"]

readingData=data.frame(user,min,conf,ft)

readingData$user=as.factor(readingData$user)
readingData$min=as.factor(readingData$min)
readingData$conf=as.factor(readingData$conf)
readingData$font_type=as.factor(readingData$font_type)
readingData$min=factor(readingData$min, levels=c(6,8,10,12,14))
readingData$conf=factor(readingData$conf, levels=c(6,8,10,12,14))

readingData=readingData%>%
  group_by(user,min, font_type)%>%
  mutate(minCounts=n())

readingData=readingData%>%
  group_by(user,conf, font_type)%>%
  mutate(confCounts=n())

summary(readingData)
```

- Groupping data 

```{r fig1,fig.width=9, fig.height=3,fig.align='center'}
##OVERALL


readTable=readingData%>%
  group_by(font_type, min)%>%
  summarise(Counts=n())

t=tibble::tribble(~font_type, ~min, ~Counts,
                          "arial",6,20,
                          "arial",8,4,
                          "arial",10,0,
                          "arial",11,0,
                          "arial",12,0,
                          "times",6,15,
                          "times",8,9,
                          "times",10,0,
                          "times",11,0,
                          "times",12,0,)

p=ggplot(t,aes(x=min, y=Counts))+
  geom_bar(stat="identity")+
  labs(title = "Minimum font size for reading (overall)")+
  xlab("Font size")+
  ylab("Counts")+
  scale_fill_discrete(name = "Font type")+
  facet_grid(~font_type)
p
```



# Writing on Pinhole Paper

## Importing data

```{r}
writtingReal=read_excel("./data/StudyD_Data.xlsx", sheet = "Writting")
```

- Formatting and grouping
```{r}
USER=writtingReal["USER"]
Q1=writtingReal["Q1"]
Q2=writtingReal["Q2"]
Q3=writtingReal["Q3"]
PEN=writtingReal["PEN"]
ACTIVITY=writtingReal["ACTIVITY"]

writtingData=data.frame(USER,Q1,Q2,Q3,PEN,ACTIVITY)


writtingData$USER=as.factor(writtingData$USER)
writtingData$Q1=as.factor(writtingData$Q1)
writtingData$Q2=as.factor(writtingData$Q2)
writtingData$Q3=as.factor(writtingData$Q3)
writtingData$PEN=as.factor(writtingData$PEN)
writtingData$ACTIVITY=as.factor(writtingData$ACTIVITY)


writtingData2=writtingData
summary(writtingData)
```
- Data visualization
- Q1: Was it hard to sign your name on perforated paper?

```{r}
ggplot(writtingData, aes(ACTIVITY))+
  geom_bar()+
  facet_grid(~PEN~Q1)
```
- Q2: Did you feel uncomfortable - perforated paper?


```{r}
ggplot(writtingData, aes(ACTIVITY))+
  geom_bar()+
  facet_grid(~PEN~Q2)
```
- Q3: Are you satisfied how it looks?
```{r}
ggplot(writtingData, aes(ACTIVITY))+
  geom_bar()+
  facet_grid(~PEN~Q3)
```

## Filtering out IDK (2) responses
```{r}
writtingData=writtingData%>%
  filter(Q1!=2)%>%
  filter(Q2!=2)%>%
  filter(Q3!=2)

summary(writtingData)

```




## GLMM Binomial
- Q1
```{r}
mQ1= glmer(Q1~PEN*ACTIVITY +(1|USER),contrasts=list(PEN='contr.sum',ACTIVITY ='contr.sum'),data = writtingData, family = binomial(link="logit"), nAGQ = 1)
summary(mQ1)
```
- Q2
```{r}
mQ2= glmer(Q2~PEN*ACTIVITY +(1|USER),contrasts=list(PEN='contr.sum',ACTIVITY ='contr.sum'), data = writtingData, family = binomial(link="logit"), nAGQ = 1)
summary(mQ2)
```
- Q3 
```{r}
mQ3= glmer(Q3~PEN*ACTIVITY +(1|USER),contrasts=list(PEN='contr.sum',ACTIVITY ='contr.sum'), data = writtingData, family = binomial(link="logit"), nAGQ = 1)
summary(mQ3)
```


## Anova
- Q1
```{r}
Anova(mQ1, type=3)
```


```{r}
Anova(mQ2, type=3)
```



```{r}
Anova(mQ3, type=3)
```




## Plots

- Readin
```{r}

## Reading plots
min=tibble::tribble(~font_type, ~min, ~Counts,
                  "arial",6,20,
                  "arial",8,4,
                  "arial",10,0,
                  "arial",12,0,
                  "arial",14,0,
                  "times",6,15,
                  "times",8,9,
                  "times",10,0,
                  "times",12,0,
                  "times",14,0,)

minFont=ggplot(min,aes(x=as.factor(min), y=Counts/0.24, fill=font_type))+
  geom_bar(stat="identity", position=position_dodge2())+
  xlab("Font size")+
  ylab("Ratio [%]")+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c( "#79797a","#cccccc"))+
  ylim(0,100)

minFont

conf=tibble::tribble(~font_type, ~conf, ~Counts,
                    "arial",6,0,
                    "arial",8,3,
                    "arial",10,14,
                    "arial",12,7,
                    "arial",14,0,
                    "times",6,0,
                    "times",8,0,
                    "times",10,12,
                    "times",12,11,
                    "times",14,1,)

confFont=ggplot(conf,aes(x=as.factor(conf), y=Counts/0.24, fill=font_type))+
  geom_bar(stat="identity", position=position_dodge2())+
  xlab("Font size")+
  ylab("Ratio [%]")+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c( "#79797a","#cccccc"))+  ylim(0,100)

confFont

figure1 <- ggarrange(minFont,confFont,
                     ncol = 2, nrow = 1)
figure1
ggplot2::ggsave("./RawPlots/segments/realPaper1.svg", figure1, width = 3, height=2, units = "in")
```


- Writting 
```{r}
### Writting plots


Q1=writtingData%>%
  group_by(Q1,PEN,ACTIVITY)%>%
  summarise(Count=n(), Percent=Count/24)%>%
  ungroup()%>%
  ggplot(aes(PEN:ACTIVITY, Percent, fill=Q1))+
  geom_bar(stat = "identity", position = "fill")+
  geom_text(
    aes(y = Percent, label = scales::percent(Percent,  accuracy = 1,)),
    position = position_stack(vjust = 0.5),
    show.legend = FALSE,
    size=3)+
  scale_fill_manual(values=c("#be1e2d","#13af4b"))+
  coord_flip()+
  theme_bw()+
  theme(legend.position = "none")
Q1

Q2=writtingData%>%
  group_by(Q2,PEN,ACTIVITY)%>%
  summarise(Count=n(), Percent=Count/24)%>%
  ungroup()%>%
  ggplot(aes(PEN:ACTIVITY, Percent, fill=Q2))+
  geom_bar(stat = "identity", position = "fill")+
  geom_text(
    aes(y = Percent, label = scales::percent(Percent,  accuracy = 1,)),
    position = position_stack(vjust = 0.5),
    show.legend = FALSE,
    size=3)+
  scale_fill_manual(values=c("#be1e2d","#13af4b", "#cccccc"))+
  coord_flip()+
  theme_bw()+
  theme(legend.position = "none")
Q2

Q3=writtingData%>%
  group_by(Q3,PEN,ACTIVITY)%>%
  summarise(Count=n(), Percent=Count/24)%>%
  ungroup()%>%
  ggplot(aes(PEN:ACTIVITY, Percent, fill=Q3))+
  geom_bar(stat = "identity", position = "fill")+
  geom_text(
    aes(y = Percent, label = scales::percent(Percent,  accuracy = 1,)),
    position = position_stack(vjust = 0.5),
    show.legend = FALSE,
    size=3)+
  scale_fill_manual(values=c("#be1e2d","#13af4b", "#cccccc"))+
  coord_flip()+
  theme_bw()+
  theme(legend.position = "none")
Q3


figure2 <- ggarrange(Q1,Q2,Q3,
                     ncol = 3, nrow = 1)
figure2

ggplot2::ggsave("./RawPlots/segments/realPaper2.svg", figure2, width = 7.27, height=2, units = "in")


```

