---
title: "Study A (Images)"
output: html_notebook
---

# Importing libs and data
```{r}
library(tidyverse)
library(ggpubr)
library(readxl)
library(gplots)
library(ggplot2)
library(dplyr)
library(rstatix)
library(reshape2)
library(lme4)
library(car)
library(flexplot)
library(multcomp)
library(lsmeans)
library(glmmTMB)
library(ggprism)
library(fitdistrplus)
```
## Formatting data 
- Select data
```{r}
imageFile<- read_excel("./data/StudyA_Data.xlsx", sheet = "DATA")
```
```{r}
USER=imageFile["USER"]
Q1=imageFile["Q1"]
Q2=imageFile["Q2"]
MOVEMENT=imageFile["MOVEMENT"]


data=data.frame(USER,Q1,Q2,MOVEMENT)
data$USER=as.factor(data$USER)
data$Q1=as.factor(data$Q1)
data$Q2=as.factor(data$Q2)
data$MOVEMENT=as.factor(data$MOVEMENT)

summary(data)
```

### Grouping data
- As this approach is subject based, we are gonna sum up the count of responses for a given mode in each question.

```{r }
details=data%>%
  group_by(USER,Q1)%>%
  summarise(Counts=n())

prefs=data%>%
  group_by(USER,Q2)%>%
  summarise(Counts=n())
```


## 1. In which  movement mode participant identify more details?
- Data overview
```{r}
summary(details)
```

 -  Inserting missing values (0)
 
```{r}
details_=dcast(details, USER~Q1, value.var="Counts",  fun.aggregate=sum) 
```
 

```{r} 
 details_ = details_%>% 
 gather(key = "Q1", value = "Counts", Circular,Linear, Same, Static) 
``` 

<!-- - Filtering out excess of zeros -->
<!-- ```{r} -->
<!-- details_filtered=details_[(details_$MOVEMENT=="LC"  & details_$Q1=="Circular" ) | (details_$MOVEMENT=="LC"  & details_$Q1=="Linear" ) | (details_$MOVEMENT=="LC"  & details_$Q1=="Same" ) | (details_$MOVEMENT=="SC"  & details_$Q1=="Circular" ) | (details_$MOVEMENT=="SC"  & details_$Q1=="Static" ) | (details_$MOVEMENT=="SC"  & details_$Q1=="Same" ) | (details_$MOVEMENT=="SL"  & details_$Q1=="Linear" ) | (details_$MOVEMENT=="SL"  & details_$Q1=="Static" ) | (details_$MOVEMENT=="SL"  & details_$Q1=="Same" ) ,]  -->
<!--  details_filtered$Q1=as.factor(details_filtered$Q1) -->
<!--  summary(details_filtered) -->
<!-- ``` -->

- Filtering out SAME responses

```{r}
details_NOSAME=details_%>%
  filter(Q1!="Same")
details_NOSAME$Q1=as.factor(details_NOSAME$Q1)
summary(details_NOSAME)
```
- Quick view
```{r fig1_1,fig.width=9, fig.height=4,fig.align='center'}
ggplot(data=details_NOSAME, aes(x=Q1,y=Counts))+
  geom_boxplot(outlier.colour="blue", outlier.shape=16,
             outlier.size=2)+
  stat_summary(color = "red")+
  xlab("Movement mode")+
  ylab("Count of votes")
```


### GLMM Binomial

- We need to use binomial since  is more robust and has less assumptions.

- Define constant -> total number of possible votes
```{r}
details_NOSAME$totalCounts=10
```

-Build the model
```{r}
mDetails=glmer(cbind(Counts, 10-Counts)~Q1 +(1|USER), data = details_NOSAME, contrasts=list(Q1='contr.sum'), family = binomial(link="logit"), nAGQ=100)
summary(mDetails)
```
### Anova
```{r}
Anova(mDetails, type=2)
```
### PWC
```{r}
pwcDetails=summary(glht(mDetails,lsm(pairwise~Q1)),test=adjusted(type="bonferroni"))
pwcDetails
```
- Manually define PWC
```{r}
pwcDetailsPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "Circular", "Static", "**",8.3,
  "Linear", "Static", "***",9.2,
)
```


## 2. What is the preferred movement mode?

- Data overview
```{r}
prefs=data%>%
  group_by(USER,Q2)%>%
  summarise(Counts=n())
summary(prefs)
```
- Inserting missing values (0)

```{r}
prefs_=dcast(prefs, USER~Q2, value.var="Counts",  fun.aggregate=sum)
```

```{r}
prefs_ = prefs_%>%
  gather(key = "Q2", value = "Counts", Circular, Linear, Same, Static)
```

- Filtering out SAME responses

```{r}
prefs_NOSAME=prefs_%>%
  filter(Q2!="Same")
prefs_NOSAME$Q2=as.factor(prefs_NOSAME$Q2)
summary(prefs_NOSAME)
```
-Data visualization

```{r fig5,fig.width=9, fig.height=4,fig.align='center'}
ggplot(data=prefs_NOSAME, aes(x=Q2,y=Counts))+
  geom_boxplot(outlier.colour="blue", outlier.shape=16,
             outlier.size=3)+
  stat_summary( color = "red") +
  # stat_summary(
  #   fun.min = function(x) mean(x) - sd(x), 
  #   fun.max = function(x) mean(x) + sd(x), 
  #   geom = "errorbar",
  #   color = "red",
  #   width = .3,
  # )+
  xlab("Movement mode")+
  ylab("Count of votes")
```


### GLMM  Binomial

- Define constant -> total number of possible votes
```{r}
prefs_NOSAME$totalCounts=10
```
- Build the model 
```{r}
mPrefs=glmer(cbind(Counts,10-Counts)~Q2 +(1|USER),contrasts=list(Q2='contr.sum'), data = prefs_NOSAME, family = binomial(link="logit"), nAGQ=100)
summary(mPrefs)
```
### Anova
```{r}
Anova(mPrefs, type=2)
```

### PWC
```{r}
pwcPrefs=summary(glht(mPrefs,lsm(pairwise~Q2)),test=adjusted(type="bonferroni"))
pwcPrefs
```
- Manually handle PWC
```{r}
pwcPrefsPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "Circular", "Linear", "***",7.6,
  #"Circular", "Static", ".",8,
  "Linear", "Static", "*",8.4,
)
```


## Generate Plots

```{r}
##Plots IMAGE
# Details 
#  In which  movement mode participant identify more details?Aka details
detailsPlot=details_NOSAME%>%
  ggplot(aes(x=Q1,y=Counts,  fill=Q1))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype = "dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1), size = 0.5)+  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x="Movement",y="Cummulative votes")+
  ylim(0,10)+
  add_pvalue(inherit.aes=FALSE,pwcDetailsPlot,
             bracket.size = 0.5,
             tip.length = 0.01,
             colour = "magenta",
             label.size=2)

detailsPlot

# Which movement mode do you prefer? aka preferences
prefsPlot=prefs_NOSAME%>%
  ggplot(aes(x=Q2,y=Counts,  fill=Q2))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype = "dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1), size = 0.5)+  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x="Movement",y="Cummulative votes")+
  ylim(0,10)+
  add_pvalue(inherit.aes=FALSE,pwcPrefsPlot,
            
             bracket.size = 0.5,
             tip.length = 0.01,
             colour = "magenta",
             label.size=2)

prefsPlot

## PREFS

figure <- ggarrange(detailsPlot, prefsPlot,
                    labels = c("(a)", "(b)"),
                    ncol = 2, nrow = 1)
figure

```




