---
title: "StudyB_1/2"
output: html_notebook
---


# Importing libs 
```{r}
library(dplyr)
library(fitdistrplus)
library(rstatix)
library(readxl)
library(lme4)
library(multcomp)
library(lsmeans)
library(car)
library(flexplot)
library(ggplot2)
library(tidyverse)
library(ggpubr)
library(ggprism)
library(reshape2)
library(ARTool)
```
# Character recognition task
## Importing file 
```{r}
charFile <- read_excel("./data/StudyB_Data.xlsx", sheet = "CHAR_Errors")
```
 
- Formatting data

```{r}
USERS<- charFile["USER"]
FS<- charFile["FONT_SIZE"]
COND=charFile["MOVEMENT"]
FT=charFile["FONT_TYPE"]
FC=charFile["FONT_CASE"]
ROTATION=charFile["ROTATION"]
E_COUNT=charFile["ERROR_COUNT"]
TRIAL=charFile["TRIAL"]


data= data.frame(USERS,FS,FT,FC,COND,E_COUNT,ROTATION, TRIAL)


data$USER <- as.factor(data$USER)
data$FONT_SIZE <- as.factor(as.numeric(data$FONT_SIZE)/4)
data$FONT_TYPE<- as.factor(data$FONT_TYPE)
data$FONT_CASE<- as.factor(data$FONT_CASE)
data$MOVEMENT <- as.factor(data$MOVEMENT)
data$ROTATION <- as.factor(data$ROTATION)
data$TRIAL <- as.factor(data$TRIAL)

data$ERROR_COUNT[is.na(data$ERROR_COUNT)] <- 0



summary(data)

```
- Groupping by user

```{r}
uData=data%>%
  group_by(USER,FONT_TYPE,MOVEMENT,FONT_CASE,FONT_SIZE)%>%
  summarise(ERROR_COUNT=sum(ERROR_COUNT))
summary(uData)
```


- Data visualization

```{r fig10,fig.width=9, fig.height=4,fig.align='center'}
hist=ggplot(uData,aes(x=ERROR_COUNT,fill=FONT_TYPE))+
  geom_bar()+
  labs(title = "Histogram")+
  xlab("Number of errors")+
  ylab("Count of errors")+
  scale_fill_discrete(name = "Font type")

hist+facet_grid(~FONT_SIZE+MOVEMENT  ~ FONT_TYPE +FONT_CASE )+labs(title = "Font size")

```


## Interaction plots


```{r}
with(uData, interaction.plot(MOVEMENT,FONT_TYPE, ERROR_COUNT, col=1:12))
```

```{r}
with(uData, interaction.plot(MOVEMENT,FONT_CASE, ERROR_COUNT, col=1:12))
```



```{r}
with(uData, interaction.plot(MOVEMENT,FONT_SIZE, ERROR_COUNT, col=1:12))
```

```{r}
with(uData, interaction.plot(MOVEMENT,interaction(FONT_TYPE, FONT_CASE), ERROR_COUNT, col=1:12))
```
```{r}
with(uData, interaction.plot(MOVEMENT,interaction(FONT_TYPE, FONT_SIZE), ERROR_COUNT, col=1:12))
```
```{r}
with(uData, interaction.plot(MOVEMENT,interaction(FONT_CASE, FONT_SIZE), ERROR_COUNT, col=1:12))
```

```{r}
with(uData, interaction.plot(MOVEMENT, interaction(FONT_TYPE, FONT_CASE, FONT_SIZE), ERROR_COUNT, col=1:12))
```
```{r}
with(uData, interaction.plot( interaction(FONT_TYPE, FONT_CASE, FONT_SIZE), MOVEMENT,ERROR_COUNT, col=1:12))
```

## GLMM Binomial
- Defining constant -> MaxErrorCount
```{r}
uData$MaxErrorCount=52
```

- Building model
```{r}
y=cbind(uData$ERROR_COUNT, 52-uData$ERROR_COUNT)
mErrorCount=glmer(y~MOVEMENT*FONT_SIZE*(FONT_CASE + FONT_TYPE)+ (1|USER), contrasts=list(MOVEMENT='contr.sum',FONT_SIZE='contr.sum', FONT_TYPE='contr.sum',FONT_CASE='contr.sum'),  data = uData, family = binomial(link="logit"), nAGQ =100,control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
```

## Anova
```{r}
Anova(mErrorCount, type = 3)
```
## PWC 
* Rebuild model to get more accurate results

- MOVEMENT MODE
```{r}
y=cbind(uData$ERROR_COUNT, 52-uData$ERROR_COUNT)
mMOVEMENT=glmer(y~MOVEMENT+ (1|USER), contrasts=list(MOVEMENT='contr.sum'),  data = uData, family = binomial(link="logit"), nAGQ =100,control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
```

- PWC
```{r}
summary(glht(mMOVEMENT,lsm(pairwise~MOVEMENT)),test=adjusted(type="bonferroni"))
```
- Manually handle pwc
```{r}
pwcMOVEMENTPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "linear", "static", "***",5.3,
  "circular", "static", "***",6,
  
)
```


- FONT SIZE
```{r}
y=cbind(uData$ERROR_COUNT, 52-uData$ERROR_COUNT)
mFS=glmer(y~FONT_SIZE+ (1|USER), contrasts=list(FONT_SIZE='contr.sum'),  data = uData, family = binomial(link="logit"), nAGQ =100,control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
```

```{r}
summary(glht(mFS,lsm(pairwise~FONT_SIZE)),test=adjusted(type="bonferroni"))
```

```{r}
pwcFONT_SIZEPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "8", "10", "***",5.3,
  "8", "12", "***",5.9,
  "10", "12", "***",6.6,
)
```

- FONT CASE
- We know this result from Anova
```{r}
pwcFONT_CASEPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "L", "U", "***",5.3,
)
```


- FONT TYPE
- We know this result from Anova
```{r}
pwcFONT_TYPEPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "A", "T", "***",5.3,
)
```

- MOVEMENT:FONT_SIZE
```{r}
y=cbind(uData$ERROR_COUNT, 52-uData$ERROR_COUNT)
mMFS=glmer(y~MOVEMENT*FONT_SIZE+ (1|USER), contrasts=list(MOVEMENT="contr.sum",FONT_SIZE='contr.sum'),  
          data = uData, family = binomial(link="logit"), nAGQ=100,
          control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
```

- Script to filter out unnecessary comparisons and to generate plot programaticallly

```{r}
pwcMFDEC=tidy(summary(glht(mMFS,lsm(pairwise~MOVEMENT*FONT_SIZE)),test=adjusted(type="bonferroni")))
##Adding starts
pwcMFDEC$adj.p.value[is.na(pwcMFDEC$adj.p.value)]=0

pwcMFDEC$p.signif=symnum(pwcMFDEC$adj.p.value, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("***", "**", "*", ".", " "))

##Adding groups
pwcMFDEC$group1=sapply(strsplit(pwcMFDEC$contrast," "), '[[',1)
pwcMFDEC$group2=sapply(strsplit(pwcMFDEC$contrast," "), '[[',4)
pwcMFDEC$C1=as.numeric(sapply(strsplit(pwcMFDEC$contrast," "), '[[',2))
pwcMFDEC$C2=as.numeric(sapply(strsplit(pwcMFDEC$contrast," "), '[[',5))

##Adding   xmin and xman
pwcMFDEC= pwcMFDEC %>% 
  mutate(xmin = case_when(C1==8~1,C1==10~2,C1==12~3))%>%
  mutate(xmin = case_when(group1=="circular"~xmin-0.25,group1=="linear"~xmin,group1=="static"~xmin+0.25))

pwcMFDEC= pwcMFDEC %>% 
  mutate(xmax = case_when(C2==8~1,C2==10~2,C2==12~3))%>%
  mutate(xmax= case_when(group2=="circular"~xmax-0.25,group2=="linear"~xmax,group2=="static"~xmax+0.25))

pwcMFDEC=pwcMFDEC%>%
  filter(pwcMFDEC$adj.p.value<0.05)

## Not same font size
pwcMFDEC=pwcMFDEC%>%
  filter(C1==C2 | group1 ==group2)



## Ordering by movement
pwcMFDEC=pwcMFDEC[order(pwcMFDEC[,10],pwcMFDEC[,10]),]

pwcMFDEC= pwcMFDEC %>% 
  mutate(color = case_when(C1==8 & C2==8~"8",C1==10& C2==10~"10",C1==12 & C2==12~"12", C1!=C2~"MX"))

##  add y.posision
#pwcMFDEC$y.position <- seq.int(4.5, by=0.2, length.out = dim(pwcMFDEC)[1])

pwcMFDEC=pwcMFDEC%>%
  group_by(color)%>%
  mutate(y.position = case_when(
    color=="MX"~seq.int(25, length.out=length(color),by=1.5),
    color!="MX"~seq.int(20, length.out=length(color),by=1.5)))

pwcMFDEC

write.csv(pwcMFDEC,'healthstudy2.csv')
```






## Plots
```{r}
# MOVEMENT
pwcMOVEMENTPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "linear", "static", "***",20,
  "circular", "static", "***",22,
  
)




movementPlot=uData%>%
  group_by(USER,MOVEMENT)%>%
  summarise(Count=sum(ERROR_COUNT))%>%
  ggplot(aes(x=MOVEMENT,y=Count,  fill=MOVEMENT))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype = "dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1), size = 0.5)+  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x="Movement",y="Error count")+
  ylim(0,30)+
  add_pvalue(inherit.aes = FALSE,pwcMOVEMENTPlot,
                   bracket.size = 0.6,
                   tip.length = 0.01,
                   colour = "magenta",
                   label.size = 7)

movementPlot





## FONT SIZE

pwcFONT_SIZEPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "8", "10", "***",23,
  "8", "12", "***",24.5,
  "10", "12", "***",26.5,
)


fsPlot=uData%>%
  group_by(USER,FONT_SIZE)%>%
  summarise(Count=sum(ERROR_COUNT))%>%
  ggplot(aes(x=FONT_SIZE,y=Count,  fill=FONT_SIZE))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line", linetype="dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1), size = 0.5)+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#cccccc", "#cccccc","#cccccc"))+
  
  labs(x="Movement",y="Error count")+
  ylim(0,30)+
  add_pvalue(inherit.aes = FALSE,pwcFONT_SIZEPlot,
             bracket.size = 0.6,
             tip.length = 0.01,
             colour = "magenta",
             label.size = 7)
fsPlot


## CASE
pwcFONT_CASEPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "L", "U", "***",25,
)

fcPlot=uData%>%
  group_by(USER,FONT_CASE)%>%
  summarise(Count=sum(ERROR_COUNT))%>%
  ggplot(aes(x=FONT_CASE,y=Count,  fill=FONT_CASE))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line",linetype="dashed", aes(group = 1)) + 
  stat_summary( color = "red", size = 0.3,aes(group = 1), size = 0.5)+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#cccccc", "#cccccc"))+
  labs(x="Movement",y="Error count")+
  ylim(0,30)+
  add_pvalue(inherit.aes = FALSE,pwcFONT_CASEPlot,
             bracket.size = 0.6,
             tip.length = 0.01,
             colour = "magenta",
             label.size = 7)
fcPlot


##FONT TYPE

pwcFONT_TYPEPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,
  "A", "T", "*",27,
)

ftPlot=uData%>%
  group_by(USER,FONT_TYPE)%>%
  summarise(Count=sum(ERROR_COUNT))%>%
  ggplot(aes(x=FONT_TYPE,y=Count,  fill=FONT_TYPE))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line",linetype="dashed", aes(group = 1)) + 
  stat_summary( color = "red",size = 0.3, aes(group = 1), size = 0.5)+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#cccccc", "#cccccc"))+
  labs(x="Movement",y="Errors")+
  ylim(0,30)+
  add_pvalue(inherit.aes = FALSE,pwcFONT_TYPEPlot,
             bracket.size = 0.6,
             tip.length = 0.01,
             colour = "magenta",
             label.size = 7)
ftPlot


## MOVEMENT:FONT_SIZE



movfsPlot=uData%>%
  group_by(USER,MOVEMENT,FONT_SIZE)%>%
  summarise(Count=sum(ERROR_COUNT))%>%
  ggplot(aes(x=FONT_SIZE,y=Count,  fill=MOVEMENT,color=MOVEMENT))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary( aes(group=MOVEMENT),
                position=position_dodge(width=0.75),color = "red", geom = "line", linetype="dashed") + 
  stat_summary( color = "red", size = 0.3,aes(group=MOVEMENT),
                position=position_dodge(width=0.75))+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  scale_color_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  
  labs(x="Movement",y="Errors")+
  ylim(0,30)+
  add_pvalue(inherit.aes=FALSE,pwcMFDEC,
             xmin = "xmin",
             xmax="xmax",
             bracket.size = 0.5,
             tip.length = 0.01,
             colour = "magenta",
             label.size=7)

movfsPlot



figure <- ggarrange(ftPlot,fcPlot,fsPlot,  movementPlot,
                    ncol = 4, nrow = 1)
figure

```

# In which movement mode was it easier to read? : Character recognition task
## Importing file
```{r}
charPrefFile <- read_excel('./data/StudyB_Data.xlsx', sheet = "CHAR_Details")
```
- Data overview
```{r}
USER=charPrefFile["USER"]
FS=charPrefFile["FONT_SIZE"]
FT=charPrefFile["FONT_TYPE"]
FC=charPrefFile["FONT_CASE"]
ROTATION=charPrefFile["ROTATION"]
PREFS=charPrefFile["Q1_REV"]
Q1=charPrefFile["Q1"]
Q2_T1=charPrefFile["Q2_T1"]
Q2_V1=charPrefFile["Q2_V1"]
colnames(charPrefFile)[15] <- "Q2_T2"

Q2_T2=charPrefFile["Q2_T2"]
Q2_V2=charPrefFile["Q2_V2"]

data= data.frame(USER,FS,FT,FC,ROTATION,Q1)

data$USER <- as.factor(data$USER)
data$FONT_SIZE <- as.factor(as.numeric(data$FONT_SIZE)/4)
data$FONT_TYPE <- as.factor(data$FONT_TYPE)
data$FONT_CASE <- as.factor(data$FONT_CASE)
data$ROTATION <- as.factor(data$ROTATION)
data$Q1<- as.factor(data$Q1)

summary(data)

```
- Groupping data 

```{r}
easier2read=data%>%
  group_by(USER,Q1, FONT_TYPE, FONT_CASE, FONT_SIZE)%>%
  summarise(Counts=n())
```
- Inserting 0 values missing
```{r}
easier2read_complete=dcast(easier2read, USER+FONT_TYPE+FONT_CASE+ FONT_SIZE~Q1, value.var="Counts",  fun.aggregate=sum)
```

```{r}
easier2read_complete = easier2read_complete%>%
  gather(key = "Q1", value = "Counts", Circular,Linear, Same, Static)
```
- Filtering out SAME responses

```{r}
easier2read_NOSAME=easier2read_complete%>%
  filter(Q1!="Same")
easier2read_NOSAME$Q1=as.factor(easier2read_NOSAME$Q1)
summary(easier2read_NOSAME)
```

- Visualization of counts
```{r fig13,fig.width=9, fig.height=4,fig.align='center'}
ggplot(easier2read_NOSAME, aes(x=Counts, fill=FONT_TYPE))+
  geom_histogram(binwidth=1)+
  facet_grid(~FONT_SIZE~Q1+FONT_CASE+FONT_TYPE)
```
## Interaction plots


```{r}
with(easier2read_NOSAME, interaction.plot(Q1,FONT_TYPE, Counts, col=1:12))
```
```{r}
with(easier2read_NOSAME, interaction.plot(Q1,FONT_CASE, Counts, col=1:12))
```
```{r}
with(easier2read_NOSAME, interaction.plot(Q1, FONT_SIZE,Counts, col=1:12))
```
```{r}
with(easier2read_NOSAME, interaction.plot(Q1,interaction(FONT_TYPE, FONT_CASE), Counts, col=1:12))
```

```{r}
with(easier2read_NOSAME, interaction.plot(Q1,interaction(FONT_TYPE, FONT_SIZE), Counts, col=1:12))
```
```{r}
with(easier2read_NOSAME, interaction.plot(Q1,interaction(FONT_CASE, FONT_SIZE), Counts, col=1:12))
```
```{r}
with(easier2read_NOSAME, interaction.plot(Q1,interaction(FONT_TYPE, FONT_CASE, FONT_SIZE), Counts, col=1:12))
```

```{r}
with(easier2read_NOSAME, interaction.plot(interaction(FONT_TYPE, FONT_CASE, Q1), interaction(FONT_SIZE), Counts, col=1:12))
```


## GLMM Binomial 
- Defining constants

```{r}
easier2read_NOSAME$totalCounts=4

```
- Building the model
```{r}
mEasier=glmer(cbind(Counts, 4-Counts)~Q1*FONT_SIZE*(FONT_CASE+FONT_TYPE)+(1|USER), data = easier2read_NOSAME, family = binomial(link="logit"), nAGQ =0, contrasts = list(Q1="contr.sum",FONT_SIZE="contr.sum",FONT_CASE="contr.sum",FONT_TYPE="contr.sum"), control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
```

## Anova
```{r}
Anova(mEasier, type = 3)
```

## PWC
```{r}
pwcEasier=summary(glht(mEasier,lsm(pairwise~Q1*FONT_SIZE*FONT_CASE+FONT_TYPE)),test=adjusted(type="holm"))

```

## PWC
- MOVEMENT
```{r}
mMOV=glmer(cbind(Counts, 4-Counts)~Q1+(1|USER), data = easier2read_NOSAME, family = binomial(link="logit"), nAGQ = 100, contrasts = list(Q1="contr.sum"))
```

```{r}
summary(glht(mMOV,lsm(pairwise~Q1)),test=adjusted(type="bonferroni"))
```

- Q1:FONT SIZE

```{r}
mQS=glmer(cbind(Counts, 4-Counts)~Q1*FONT_SIZE+(1|USER), data = easier2read_NOSAME, family = binomial(link="logit"), nAGQ = 100, contrasts = list(Q1="contr.sum", FONT_SIZE="contr.sum"))
```


```{r}
pwcQSIZEPlot=tidy(summary(glht(mQS,lsm(pairwise~Q1*FONT_SIZE)),test=adjusted(type="bonferroni"))
)
##Adding starts

pwcQSIZEPlot$p.signif=symnum(pwcQSIZEPlot$adj.p.value, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("***", "**", "*", ".", " "))
pwcQSIZEPlot$row_num <- seq.int(nrow(pwcQSIZEPlot))

##Adding groups
pwcQSIZEPlot$group1=sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',1)
pwcQSIZEPlot$group2=sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',4)
pwcQSIZEPlot$C1=as.numeric(sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',2))
pwcQSIZEPlot$C2=as.numeric(sapply(strsplit(pwcQSIZEPlot$contrast," "), '[[',5))

##Adding   xmin and xman
pwcQSIZEPlot= pwcQSIZEPlot %>% 
  mutate(xmin = case_when(C1==8~1,C1==10~2,C1==12~3))%>%
  mutate(xmin = case_when(group1=="Circular"~xmin-0.25,group1=="Linear"~xmin,group1=="Static"~xmin+0.25))

pwcQSIZEPlot= pwcQSIZEPlot %>% 
  mutate(xmax = case_when(C2==8~1,C2==10~2,C2==12~3))%>%
  mutate(xmax= case_when(group2=="Circular"~xmax-0.25,group2=="Linear"~xmax,group2=="Static"~xmax+0.25))

## Not significatt values fitered out
pwcQSIZEPlot=pwcQSIZEPlot%>%
  filter(adj.p.value<0.05)

## Not same font size
pwcQSIZEPlot=pwcQSIZEPlot%>%
  filter(C1==C2 | group1 ==group2)


## Ordering by movement
pwcQSIZEPlot=pwcQSIZEPlot[order(pwcQSIZEPlot[,11],pwcQSIZEPlot[,11]),]

pwcQSIZEPlot= pwcQSIZEPlot %>% 
  mutate(color = case_when(C1==8 & C2==8~"8",C1==10& C2==10~"10",C1==12 & C2==12~"12", C1!=C2~"MX"))



##  add y.posision
#pwcQSIZEPlot$y.position <- seq.int(4.5, by=0.2, length.out = dim(pwcQSIZEPlot)[1])

pwcQSIZEPlot=pwcQSIZEPlot%>%
  group_by(color)%>%
  mutate(y.position = case_when(
    color=="MX"~seq.int(17.5, length.out=length(color),by=0.75),
    color!="MX"~seq.int(16.5, length.out=length(color),by=0.75)))

pwcQSIZEPlot
```

- Q1:FONT_TYPE

```{r}
mQFT=glmer(cbind(Counts, 4-Counts)~Q1*FONT_TYPE+(1|USER), data = easier2read_NOSAME, family = binomial(link="logit"), nAGQ = 100, contrasts = list(Q1="contr.sum", FONT_TYPE="contr.sum"))
```


```{r}
pwcQCASEPlot=tidy(summary(glht(mQFT,lsm(pairwise~Q1*FONT_TYPE)),test=adjusted(type="bonferroni"))
)
##Adding starts

pwcQCASEPlot$p.signif=symnum(pwcQCASEPlot$adj.p.value, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("***", "**", "*", ".", " "))
pwcQCASEPlot$row_num <- seq.int(nrow(pwcQCASEPlot))

##Adding groups
pwcQCASEPlot$group1=sapply(strsplit(pwcQCASEPlot$contrast," "), '[[',1)
pwcQCASEPlot$group2=sapply(strsplit(pwcQCASEPlot$contrast," "), '[[',4)
pwcQCASEPlot$C1=sapply(strsplit(pwcQCASEPlot$contrast," "), '[[',2)
pwcQCASEPlot$C2=sapply(strsplit(pwcQCASEPlot$contrast," "), '[[',5)

##Adding   xmin and xman
pwcQCASEPlot= pwcQCASEPlot %>% 
  mutate(xmin = case_when(C1=="A"~1,C1=="T"~2))%>%
  mutate(xmin = case_when(group1=="Circular"~xmin-0.25,group1=="Linear"~xmin,group1=="Static"~xmin+0.25))

pwcQCASEPlot= pwcQCASEPlot %>% 
  mutate(xmax = case_when(C2=="A"~1,C2=="T"~2))%>%
  mutate(xmax= case_when(group2=="Circular"~xmax-0.25,group2=="Linear"~xmax,group2=="Static"~xmax+0.25))

pwcQCASEPlot= pwcQCASEPlot %>% 
  mutate(color = case_when(C1=="A"& C2=="A"~"A",C1=="T"& C2=="T"~"T", C1!=C2~"AT"))


## Not significatt values fitered out
pwcQCASEPlot=pwcQCASEPlot%>%
  filter(adj.p.value<0.05)



## Not significatt values fitered out
pwcQCASEPlot=pwcQCASEPlot%>%
  filter(C1==C2 | group1 == group2)

## Ordering by movement
pwcQCASEPlot=pwcQCASEPlot[order(pwcQCASEPlot[,11],pwcQCASEPlot[,12]),]
##  add y.posision
#pwcQCASEPlot$y.position <- seq.int(4.2, by=0.2, length.out = dim(pwcQCASEPlot)[1])
pwcQCASEPlot=pwcQCASEPlot%>%
  group_by(color)%>%
  mutate(y.position = case_when(
    color=="AT"~seq.int(26.5, length.out=length(color),by=0.75),
    color!="AT"~seq.int(24.5, length.out=length(color),by=0.75)))

pwcQCASEPlot
```

```{r fig14_5,fig.width=9, fig.height=4,fig.align='center'}
ggplot(data=easier2read_NOSAME, aes(x=FONT_CASE,y=Counts, color=Q1))+
  geom_boxplot(outlier.colour="blue", outlier.shape=16,
             outlier.size=2)+
  xlab("Font case")+
  ylab("Votes")+
   add_pvalue(pwcQCASEPlot,
              xmin = "xmin",
             xmax="xmax",
             bracket.size = 0.5,
             tip.length = 0.01,
             colour = "color",
             label.size =4)+
stat_summary(fun = mean,
              aes(group=Q1, col=Q1),
              position=position_dodge(width=0.75),
              color = "red") +
  stat_summary(
    fun.min = function(x) mean(x) - sd(x),
    fun.max = function(x) mean(x) + sd(x),
    geom = "errorbar",
    color = "red",
    width = .3,
    alpha=0.5,
    aes(group=Q1, col=Q1) , position=position_dodge(width=0.75)
  
  )+
  scale_x_discrete(labels=c("Lower", "Upper"))+
  scale_color_discrete(name="Movement",limits=c("Circular", "Linear", "Static"))
```

## Plots 
```{r}

## MOVEMENT
pwcMOVPlot=tibble::tribble(
  ~group1,~group2,~p.signif,~y.position,~FONT_SIZE,~C1,~C2,~xmin,~xmax,
  "Circular", "Linear", "***",38,2,0,0,1,2,
  "Circular", "Static", "***", 44,2,0,0,1,3,
  "Linear", "Static", "***", 42,2,0,0,2,3,
)



movPLot=easier2read_NOSAME%>%
  group_by(USER,Q1)%>%
  summarise(Count=sum(Counts))%>%
  ggplot(aes(x=Q1,y=Count,  fill=Q1))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary(color = "red", geom = "line",linetype="dashed", aes(group = 1)) + 
  stat_summary( color = "red",size = 0.3, aes(group = 1), size = 0.5)+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  labs(x=NA,y="Cummulative votes")+
  ylim(0,45)+
  add_pvalue(inherit.aes = FALSE,pwcMOVPlot,
             bracket.size = 0.6,
             tip.length = 0.01,
             colour = "magenta",
             label.size = 6)

movPLot


movfsPlot=easier2read_NOSAME%>%
  group_by(USER,Q1,FONT_SIZE)%>%
  summarise(Count=sum(Counts))%>%
  ggplot(aes(x=FONT_SIZE,y=Count,  fill=Q1))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary( aes(group=Q1),
                position=position_dodge(width=0.75),color = "red", geom = "line", linetype="dashed") + 
  stat_summary( color = "red", size = 0.3,aes(group=Q1),
                position=position_dodge(width=0.75))+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+

  labs(x="Movement",y="Errors")+
  ylim(0,45)+
  add_pvalue(inherit.aes=FALSE,pwcQSIZEPlot,
             xmin = "xmin",
             xmax="xmax",
             bracket.size = 0.5,
             tip.length = 0.01,
             colour = "magenta",
             label.size=2)

movfsPlot



movftPlot=easier2read_NOSAME%>%
  group_by(USER,Q1,FONT_TYPE)%>%
  summarise(Count=sum(Counts))%>%
  ggplot(aes(x=FONT_TYPE,y=Count,  fill=Q1))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position=position_jitterdodge(),alpha=0.5,stroke = 0)+
  stat_summary( aes(group=Q1),
                position=position_dodge(width=0.75),color = "red", geom = "line", linetype="dashed") + 
  stat_summary( color = "red", size = 0.3,aes(group=Q1),
                position=position_dodge(width=0.75))+
  theme_bw()+
  theme(legend.position = "none")+ 
  scale_fill_manual(values=c("#4d5b95", "#79797a", "#f4b979"))+
  
  labs(x="Movement",y="Errors")+
  ylim(0,45)+
  add_pvalue(inherit.aes=FALSE,pwcQCASEPlot,
             xmin = "xmin",
             xmax="xmax",
             bracket.size = 0.5,
             tip.length = 0.01,
             colour = "magenta",
             label.size=2)

movftPlot


movPLot

figure1 <- ggarrange(movPLot,movftPlot,
                    labels = c("(a)", "(b)"),
                    ncol = 2, nrow = 1)
figure1

ggplot2::ggsave("./RawPlots/segments/Q11.svg", movPLot, width = 2, height=3, units = "in")
ggplot2::ggsave("./RawPlots/segments/Q12.svg", movftPlot, width = 3, height=3, units = "in")
ggplot2::ggsave("./RawPlots/segments/Q13.svg", movfsPlot, width = 4.27, height=3, units = "in")

```

